---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r ggplot2, echo=TRUE}
require(ggplot2)
library (ggplot2)
#1.1
 setwd('C:\\Users\\Alexandre\\Documents\\DataAnalysisScripts\\Reproducible Research')
activity <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
```{r mean, echo=TRUE}
#1
StepsByDate<-aggregate(. ~ date, data=activity, FUN = sum)
#2
with(StepsByDate,qplot(steps, geom="histogram",main = "Histogram of Number of Steps By Day"))
#3
mean(StepsByDate$steps)
median(StepsByDate$steps)

```

## What is the average daily activity pattern?

```{r pattern, echo=TRUE}
#1
meanOfStepsByInterval<-aggregate(steps ~ interval, data=activity, FUN = mean)
with(meanOfStepsByInterval,qplot(x=interval,y=steps,geom = 'line',main = 'average number of steps taken by interval'))

#2
meanOfStepsByInterval[which.max(meanOfStepsByInterval$steps),]
```
The 5-minute interval that contains the maximum number of steps is the interval 835


## Imputing missing values
The Number of NA's is:
```{r part4, echo=TRUE}

#1
sum(is.na(activity))
```
I substitute by the mean of steps by interval of all the days. (this info was calculated in the previous question)
```{r part4-2, echo=TRUE}

#2

listOfNA<-is.na(activity)

justNARows<-which(listOfNA==TRUE)

newDataSet<-activity

for (i in justNARows){
  rowOfInterval<-which(meanOfStepsByInterval$interval==activity[i,'interval'])
  newDataSet[i,'steps']<-meanOfStepsByInterval[rowOfInterval,'steps']
  
}
```
Creating The DataSet...
```{r part4-3, echo=TRUE}
#3

StepsByDateNewData<-aggregate(steps ~ date, data=newDataSet, FUN = sum)
```
Histogram and Mean and Median.
```{r part4-4, echo=TRUE}
#4.4
with(StepsByDateNewData,qplot(steps, geom="histogram",main = "New Histogram of Number of Steps By Day"))

summary(StepsByDateNewData$steps)

summary(StepsByDate$steps)
```

As we can see, the Median is now different.


## Are there differences in activity patterns between weekdays and weekends?

Creating the factor variable
```{r lubridate, echo=TRUE}
require(lubridate)
library(lubridate)
weekdays(ymd(activity[1,'date']),abbreviate = TRUE)

weekFactor <- as.factor(c('WeekDay','WeekEnd'))
activity$week<-weekFactor[1]

weekDays <- c("seg","ter","qua","qui","sex")
for (i in 1:dim(activity)[1]){
  if (weekdays(ymd(activity[i,'date']),abbreviate = TRUE) %in% weekDays){
    activity[i,'week'] <- 'WeekDay'
  }else{
    activity[i,'week'] <- 'WeekEnd'
    
  }

}
```

The plot containing a time series of the 5-minute interval and the average number of steps taken, averaged across all weekday days or weekend days.

```{r, echo=TRUE}

finalData<-aggregate(steps ~ week + interval, data=activity,FUN=mean)

qplot(data = finalData, x=interval,y=steps,geom='line',facets = week~.)

```

